Radio Crickets: Chirping Jets from Black Hole Binaries Entering their Gravitational Wave Inspiral

### 2015-12-02 Paper/paper.tex
Thank the referee

We acknowledge useful discussions with Martin Haehnelt, Enrico
Ramirez-Ruiz and Alberto Rorai.  This work was supported in part by
NSF grant AST-1312034 (for A.~L.).  G.~K. gratefully acknowledges
support by he FP7 ERC Advanced Grant Emergence-320596.

>>>>

We acknowledge helpful comments from the anonymous referee and useful
discussions with Martin Haehnelt, Enrico Ramirez-Ruiz and Alberto
Rorai.  This work was supported in part by NSF grant AST-1312034 (for
A.~L.) and by the FP7 ERC Advanced Grant Emergence-320596 (for G.~K.).
